---
title: "Succession and Flowering Time "
subtitle: "G. Custer 5-7-20"
output: html_notebook
---
Below is a link to the reasoning for same statistics for strata argument. 
http://r-sig-ecology.471788.n2.nabble.com/Adonis-output-with-or-without-strata-td7580521.html
```{r}
library(ggplot2) 
library(phyloseq)
library(gridExtra)
library(EnvStats)
library(FSA)
library(parallelDist)
library(pairwiseAdonis)
library(ggordiplots)
library(tidyverse)
library(vegan)
library(RColorBrewer)
```

Load environment from dada2 
```{r}
#loaded original and then subset to only what we needed to keep
#load("~/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/MicroFloweringTime_Env.RData")
load("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/May_Revision/R_Data/Sucession_&_Flowering_Time_PS.RData")
```

This has already been ran and saved in the R environment that is included. 
```{#r}
## MERGING INTO PHYLOSEQ OBJECT
data <- merge_phyloseq(OTU,TAX,MAP)
data
```

Subsetting to non-bacterial taxa in case this would be of interest later. 
```{r}
## LOOKING AT CONTAMINATION AND UNASSIGNED SEQUENCES
mitochondria_contaminants <- subset_taxa(data, Family == "Mitochondria") ## 118 ASVs of Mitochondria
archaea_contaminants <- subset_taxa(data, Kingdom == "Archaea") ## 5 ASVs of Archaea
#chloroplast_contaminants <- subset_taxa(data, Class == "Chloroplast")
chloroplast_contaminants <- subset_taxa(data, Order == "Chloroplast") ## 104 chloroplasts
eukaryota_contaminants <- subset_taxa(data, Kingdom == "Eukaryota")  ## 42 eukaryotic ASVs
sequences_not_assigned_to_kingdom <- subset_taxa(data, is.na(Kingdom)) ##drop 37 ASVs not assigned at Kingdom level
# ntaxa(chloroplast_contaminants)
```

Keep only bacterial taxa. 
```{r}
data.bac <- subset_taxa(data, Kingdom == "Bacteria")
```

Transform and rarefy
```{r}
#rarefy to 77213 reads for alpha diversity calculations
data_rarefied <- rarefy_even_depth(data.bac, sample.size= 77213, rngseed=(12), replace=F)
#5 Samples removed
#transform
data_transformed <- transform_sample_counts(data.bac, function(x) x / sum(x) )
#Run these to see how many samples and taxa are included in each object
data.bac
data_rarefied
data_transformed
```

##Alpha Diversity
Calculate, statistical tests, and graphing of alpha diversity metrics
```{r}
#Prep data and create a dataframe to run statistics on
mic.assmblg <- data_rarefied
results <- estimate_richness(mic.assmblg, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(mic.assmblg)
```

Alpha diversity by time point
```{r}
#get colors for graphs
display.brewer.pal(n = 8, name = 'Dark2')
brewer.pal(n = 8, name = "Dark2")

#Alpha diversity calculations by time point
timept <- plot_richness(mic.assmblg, x = "Sampling_time", measures=c("Shannon","Simpson", "Observed"), color='Sampling_time') + guides(color=guide_legend(title="Sampling Time"))#, shape="Sampling_time")
timept <- timept + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=10, angle=0),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Sampling Time") + theme(axis.text=element_text(size=12)) 
timept<-timept + scale_colour_manual(values = c( "#1B9E77", "#D95F02", "#7570B3", "#E7298A"))
timept

ggsave("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/Final_Figures/Figure3A.tiff", device = "tiff") 
#non parametric testing of alpha diversity by time point
tp_shannon<-kruskal.test(results$Shannon~ factor(d$Sampling_time))
dunnTest(results$Shannon~ factor(d$Sampling_time), method = "bon")

tp_simpson<-kruskal.test(results$Simpson~ factor(d$Sampling_time))
dunnTest(results$Simpson~ factor(d$Sampling_time), method = "bon")

tp_observed<-kruskal.test(results$Observed~ factor(d$Sampling_time))
dunnTest(results$Observed~ factor(d$Sampling_time), method = "bon")
```

Alpha diversity by phenotype (wild-type, early or late flowering)
```{r}
#by flowering time
ft <- plot_richness(mic.assmblg, x = "phenotype", measures=c("Shannon","Simpson", "Observed"), color='phenotype')
ft <- ft + geom_boxplot() + theme_bw()
ft

#Statistical testing of alpha diversity by phenotypes
tp_shannon<-kruskal.test(results$Shannon~ factor(d$phenotype))
dunnTest(results$Shannon~ factor(d$phenotype), method = "bon")

tp_simpson<-kruskal.test(results$Simpson~ factor(d$phenotype))
dunnTest(results$Simpson~ factor(d$phenotype), method = "bon")

tp_observed<-kruskal.test(results$Observed~ factor(d$phenotype))
dunnTest(results$Observed~ factor(d$phenotype), method = "bon")
```

Alpha diversity by plant genotypes at time point 1. This allows us to say that they were similar at the beginning, so differences were likely due to flowering time or time since germination. 
```{r}
#Create a new label that includes both pheno and genoptype in one label (Geno_Pheno)
#genotype
sample_data(mic.assmblg)$genotype_base <-  factor(sample_data(mic.assmblg)$genotype_base, levels = c( "CS3797", "SALK_072930C", "CS6673", "CS6230", "CS9869"), ordered = T)
#Create new label with both genotype and phenotype
sample_data(mic.assmblg)$Genotype <-  factor(sample_data(mic.assmblg)$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

#subset to time point 1
mic.assmblg_T1<-subset_samples(mic.assmblg, Sampling_time == "T1")

geno <- plot_richness(mic.assmblg_T1, x = "genotype_base", measures=c("Shannon","Simpson", "Observed"), color='Genotype') + guides(color=guide_legend(title="Genotype"))
geno <- geno + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=8, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Genotype") + theme(axis.text=element_text(size=12)) 
geno <- geno + scale_colour_manual(values = c( "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2"))
geno
ggsave("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/Final_Figures/Figure2A.tiff", device = "tiff") 


#Calculate alpha diversity metrics at time point 1
results_t1 <- estimate_richness(mic.assmblg_T1, measures = c('Shannon', 'Simpson', 'Observed'))
d_t1 <- sample_data(mic.assmblg_T1)

#Statistical tests of alpha diversity at time point 1
tp_shannon<-kruskal.test(results_t1$Shannon~ factor(d_t1$genotype))
dunnTest(results_t1$Shannon~ factor(d_t1$genotype), method = "bon")

tp_simpson<-kruskal.test(results_t1$Simpson~ factor(d_t1$genotype))
dunnTest(results_t1$Simpson~ factor(d_t1$genotype), method = "bon")

tp_observed<-kruskal.test(results_t1$Observed~ factor(d_t1$genotype))
dunnTest(results_t1$Observed~ factor(d_t1$genotype), method = "bon")
```

Alpha diversity of developmental stage 
```{r}
#set up color palette
display.brewer.all(colorblindFriendly = F)
display.brewer.pal(n = 8, name = 'Accent')
brewer.pal(n = 8, name = "Accent")

#calculae alpha diversity metrics
sample_data(mic.assmblg)$Developmental_stage <-  factor(sample_data(mic.assmblg)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting", "senesce"), ordered = T)
#by genotype
status <- plot_richness(mic.assmblg, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') + guides(color=guide_legend(title="Developmental Stage"))#, shape="Sampling_time")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
status <- status + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=8, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Developmental Stage") + theme(axis.text=element_text(size=12)) 
status <- status +scale_colour_manual(values = c("#7FC97F", "#BEAED4", "#FDC086", "#386CB0"))
status

ggsave("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/Final_Figures/Figure4A.tiff", device = "tiff") 
#rotate axis

tp_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

tp_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

tp_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")
```

##Multivariate analyses - Beta-diversity
Prepare data frame for multivariate analyses
```{r}
#extract relevant data: OTU table and Metadata
taxa_table<-data.frame(otu_table(data_transformed))
samp_data <- data.frame(sample_data(data_transformed))
#ordinate 
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)
```

Adonis testing and ordination by Time point
```{r}
#Run adonis for sampling time
adonis(psdist ~ Sampling_time, data.frame((samp_data)), permutations = 1000)
#pairwise adonis 
pairwise<-pairwise.adonis2(taxa_table ~ Sampling_time, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
summary(pairwise)
pairwise

#create a column that contains both genotpye and phenotype for graphing purposes.
samp_data$Genotype <-  factor(samp_data$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

#make the plot with everything on it and we can subset from there. 
d <- gg_ordiplot(ord, samp_data$Sampling_time, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#Extract the ellipses from the gg_ordiplot ordination
df_ellipse <- d$df_ellipse
ellipseT1 <- subset(df_ellipse, Group == "T1", droplevels= TRUE)
ellipseT2 <- subset(df_ellipse, Group == "T2", droplevels= TRUE)
ellipseT3 <- subset(df_ellipse, Group == "T3", droplevels= TRUE)
ellipseT4 <- subset(df_ellipse, Group == "T4", droplevels= TRUE)

#make the dataframe and and rename for manual plotting with ggplot
test<-d$df_ord
test$Sample_ID<-rownames(test)
dat<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(dat)<-c("Group", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, dat)
names(test)<-c("x", "y","Time","SampleID", "Phenotype", "Genotype")

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Time)  + geom_point(aes(color= Time, shape=Genotype)) + scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipseT1, aes(x=x, y=y), color="#1B9E77", linetype="solid", size=1.0) +
    geom_path(data= ellipseT2, aes(x=x, y=y), color="#D95F02", linetype="solid", size=1.0) +
  geom_path(data= ellipseT3, aes(x=x, y=y), color="#7570B3", linetype="solid", size=1.0) +
    geom_path(data= ellipseT4, aes(x=x, y=y), color="#E7298A", linetype="solid", size=1.0) 

plot_test<- plot_test + theme_classic()
m<-plot_test 
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Time: p < 0.001")
m <- m + labs(x= "NMDS2", y="NMDS1")
t <- m 
t

ggsave("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/Final_Figures/Figure3B.tiff", device = "tiff") 
```

This can be used to subset to individual time points. 
```{r}
#run this if we want to subset to time 1 and look at beta diversity among genotypes at time 1 like we did for the alpha diversity. 
data_transformed_t1<-subset_samples(data_transformed, Sampling_time =="T1")
taxa_table<-data.frame(otu_table(data_transformed_t1))
samp_data <- data.frame(sample_data(data_transformed_t1))
psdist_t1<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)

adonis(psdist ~ Genotype, data = data.frame((samp_data)), permutations = 100)
#not significant so no need to do pairwise comparisons. 

#create column with genotype and phenotype
samp_data$Genotype <-  factor(samp_data$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

#make the plot with everything on it and we can subset from there. 
d <- gg_ordiplot(ord, samp_data$Genotype, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipseG1 <- subset(df_ellipse, Group == "CS3797 (TFL2-2, early)", droplevels= TRUE)
ellipseG2 <- subset(df_ellipse, Group == "CS6230 (AP1-10, late)", droplevels= TRUE)
ellipseG3 <- subset(df_ellipse, Group == "CS6673 (WT, WT)", droplevels= TRUE)
ellipseG4 <- subset(df_ellipse, Group == "CS9869 (FT-10, late)", droplevels= TRUE)
ellipseG5 <- subset(df_ellipse, Group == "SALK_072930C (SVP-32, early)", droplevels= TRUE)

#make the dataframe and and rename for manual plotting with ggplot
test<-d$df_ord
test$Sample_ID<-rownames(test)
dat<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(dat)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, dat)
names(test)<-c("x", "y","Genotype","SampleID", "Time", "Phenotype", "Genotype2")

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Genotype)  + scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")) + geom_point(aes(color= Genotype))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
    geom_path(data= ellipseG1, aes(x=x, y=y), color="#E69F00", linetype="solid", size=1.0) +
    geom_path(data= ellipseG2, aes(x=x, y=y), color="#56B4E9", linetype="solid", size=1.0) +
    geom_path(data= ellipseG3, aes(x=x, y=y), color="#009E73", linetype="solid", size=1.0) +
    geom_path(data= ellipseG4, aes(x=x, y=y), color="#F0E442", linetype="solid", size=1.0) +
    geom_path(data= ellipseG5, aes(x=x, y=y), color="#0072B2", linetype="solid", size=1.0) 

plot_test<- plot_test + theme_classic()
m<-plot_test 

m <-m + annotate("text", x = 0.225, y = -0.34, label = "Genoptype: p  > 0.7")
m<- m + labs(x= "NMDS2", y="NMDS1")
g <- m 
g

ggsave("/Users/gordoncuster/Desktop/Manuscript Submissions/Published/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/Final_Figures/Figure2B.tiff", device = "tiff") 
```
Phenotype
```{r}
adonis(psdist ~  phenotype, data = data.frame((samp_data)), permutations = 100)
#not significant so no need to do pairwise comparisons. 

#make the plot with everything on it and we can subset from there. 
d <- gg_ordiplot(ord, samp_data$phenotype, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipsep1 <- subset(df_ellipse, Group == "early", droplevels= TRUE)
ellipsep2 <- subset(df_ellipse, Group == "late", droplevels= TRUE)
ellipsep3 <- subset(df_ellipse, Group == "WT", droplevels= TRUE)

#make the dataframe and and rename for manual plotting with ggplot
test<-d$df_ord
test$Sample_ID<-rownames(test)
dat<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(dat)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, dat)
names(test)<-c("x", "y","phenotype2","SampleID", "Time", "Phenotype", "Genotype")

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Phenotype) + scale_color_manual(values=c("#F564E3", "#619CFF", "#F8766D", "#009E73", "#000000")) + geom_point(aes(color=Phenotype, shape = Genotype))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipsep1, aes(x=x, y=y), color="#F564E3", linetype="solid", size=1.0) +
    geom_path(data= ellipsep2, aes(x=x, y=y), color="#619CFF", linetype="solid", size=1.0) +
    geom_path(data= ellipsep3, aes(x=x, y=y), color="#F8766D", linetype="solid", size=1.0) 
   
plot_test<- plot_test + theme_classic()
m<-plot_test 
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Time: P  = 0.27")
m<- m + labs(x= "NMDS2", y="NMDS1")
p <- m + ggtitle("Ordination by Phenotype") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
p
```

Flowering Status
```{r}
adonis(psdist ~  Sampling_time, data= data.frame((samp_data)), permutations = 1000)
pairwise<-pairwise.adonis2(taxa_table ~ Developmental_stage, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
summary(pairwise)
pairwise

#make the plot with everything and go from there
d <- gg_ordiplot(ord, samp_data$Developmental_stage, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipses1 <- subset(df_ellipse, Group == "senesce", droplevels= TRUE)
ellipses2 <- subset(df_ellipse, Group == "flowering", droplevels= TRUE)
ellipses3 <- subset(df_ellipse, Group == "fruiting", droplevels= TRUE)
ellipses5 <- subset(df_ellipse, Group == "vegetative", droplevels= TRUE)

#make the dataframe and and rename for manual plotting with ggplot
test<-d$df_ord
test$Sample_ID<-rownames(test)
dat<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(dat)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, dat)
#test$Group=NULL
names(test)<-c("x", "y","Developmental Stage","SampleID", "Time", "Phenotype", "Genotype")
test$`Developmental Stage` <- factor(test$`Developmental Stage`, levels = c("vegetative",  "flowering", "fruiting","senesce"))
#make the ggplot scatter plot
#plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Developmental_stage) + scale_color_manual(values=c("#F564E3", "#619CFF", "#FDC086", "#386CB0")) + geom_point(aes(color= Developmental_stage, shape=Time))
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=`Developmental Stage`) + scale_color_manual(values=c("#7FC97F", "#BEAED4", "#F8766D","#386CB0" )) + geom_point(aes(color= `Developmental Stage`, shape=Time))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipses1, aes(x=x, y=y), color="#7FC97F", linetype="solid", size=1.0) +
    geom_path(data= ellipses2, aes(x=x, y=y), color="#BEAED4", linetype="solid", size=1.0) +
    geom_path(data= ellipses3, aes(x=x, y=y), color="#FDC086", linetype="solid", size=1.0) +
    geom_path(data= ellipses5, aes(x=x, y=y), color="#386CB0", linetype="solid", size=1.0) 
   
plot_test<- plot_test + theme_classic()
m<-plot_test 
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Developmental Stage: p < 0.01")
m<- m + labs(x= "NMDS2", y="NMDS1")
s <- m 
s
```

```{r}
grid.arrange(t, s, p, g)
```

##Strata argument for nesting of analyses
testing with nesting by developmental stage or by sampling time
```{r}
adonis(psdist ~ Sampling_time, data= data.frame((samp_data)), strata = samp_data$Developmental_stage, permutations = 1000)
adonis(psdist ~ Sampling_time, data= data.frame((samp_data)), permutations = 1000)

adonis(psdist ~ Developmental_stage, data= data.frame((samp_data)), strata = samp_data$Sampling_time, permutations = 1000)
adonis(psdist ~ Developmental_stage, data= data.frame((samp_data)), permutations = 1000)

```

#Split by time point and examine flowering status at each time point. 
```{r}
time1<- subset_samples(data_rarefied, Sampling_time == "T1")
time2<- subset_samples(data_rarefied, Sampling_time == "T2")
time3<- subset_samples(data_rarefied, Sampling_time == "T3")
time4<- subset_samples(data_rarefied, Sampling_time == "T4")

time1_t<- subset_samples(data_transformed, Sampling_time == "T1")
time2_t<- subset_samples(data_transformed, Sampling_time == "T2")
time3_t<- subset_samples(data_transformed, Sampling_time == "T3")
time4_t<- subset_samples(data_transformed, Sampling_time == "T4")
```

Diversity (alpha and beta) split by time point and examining impact of Developmental stage 
Time 1
```{r}
mic.assmblg <- time1
results <- estimate_richness(time1, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time1)

#sample_data(time1)$status <-  factor(sample_data(time1)$status, levels = c("veg", "preflwr"), ordered = T)

#by time point
time1_status_alpha <- plot_richness(time1, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time1_status_alpha <- time1_status_alpha + geom_boxplot() + theme_bw()
time1_status_alpha

#At time 1 All samples are in the same developmental stage so no need for statistical testing. 
```
Time 2
```{r}
mic.assmblg <- time2
results <- estimate_richness(time2, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time2)

sample_data(time2)$Developmental_stage <-  factor(sample_data(time2)$Developmental_stage, levels = c("vegetative", "flowering"), ordered = T)


#by time point 2 
time2_status_alpha <- plot_richness(time2, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time2_status_alpha <- time2_status_alpha + geom_boxplot() + theme_bw()
time2_status_alpha


t2_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

t2_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

t2_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")



taxa_table<-data.frame(otu_table(time2_t))
samp_data <- data.frame(sample_data(time2_t))
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 1000, previous.best = T)
stressplot(ord)

adonis(psdist ~  Developmental_stage , data = data.frame((samp_data)))
```

Time 3
```{r}
mic.assmblg <- time3
results <- estimate_richness(time3, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time3)

sample_data(time3)$Developmental_stage <-  factor(sample_data(time3)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting"), ordered = T)

#by time point
time3_status_alpha <- plot_richness(time3, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
time3_status_alpha <- time3_status_alpha + geom_boxplot() + theme_bw()
time3_status_alpha

t3_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

t3_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

t3_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")


taxa_table<-data.frame(otu_table(time3_t))
samp_data <- sample_data(time3_t)
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)

adonis(psdist ~  Developmental_stage , data = data.frame((samp_data)))

```

Time 4
```{r}
mic.assmblg <- time4
results <- estimate_richness(time4, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time4)

sample_data(time4)$Developmental_stage <-  factor(sample_data(time4)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting", "senesce"), ordered = T)

#by time point
time4_status_alpha <- plot_richness(time4, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
time4_status_alpha <- time4_status_alpha + geom_boxplot() + theme_bw()
time4_status_alpha

#shapiro.test(aov(results$Shannon~d$time_point)$residuals)
t4_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

t4_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

t4_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")


taxa_table<-data.frame(otu_table(time4_t))
samp_data <- sample_data(time4_t)
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)

adonis(psdist ~  Developmental_stage , data = data.frame((samp_data)), permutations = 1000)
pairwise<-pairwise.adonis2(taxa_table ~ Developmental_stage, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
pairwise
```
