---
title: "Succession and Flowering Time"
subtitle: "G. Custer 5-7-20"
output: html_notebook
---

```{r}
library(ggplot2) 
library(phyloseq)
library(gridExtra)
library(EnvStats)
library(FSA)
library(parallelDist)
library(pairwiseAdonis)
library(ggordiplots)
library(tidyverse)
library(vegan)
library(RColorBrewer)
```

Load environemnt
```{r}
#loaded original and then subset to only what we needed to keep
#load("~/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/MicroFloweringTime_Env.RData")
load("/Users/gordoncuster/Desktop/Manuscript Submissions/In Review/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/GC_SFT_May2020.RData")

```
read in new metadata
```{r}
meta_data<-read.csv("/Users/gordoncuster/Desktop/Manuscript Submissions/In Review/SuccessionFloweringTime/SuccessionFloweringTime/METADATA_successionVdevelop_7May20.csv")
rownames(meta_data) <- meta_data$sampleID
meta_data$Sample=NULL
MAP =  sample_data(meta_data)
```

```{r}
## MERGING INTO PHYLOSEQ OBJECT
data <- merge_phyloseq(OTU,TAX,MAP)
data
```

Subsetting to non-bacterial taxa
```{r}
## LOOKING AT CONTAMINATION AND UNASSIGNED SEQUENCES
mitochondria_contaminants <- subset_taxa(data, Family == "Mitochondria") ## 118 ASVs of Mitochondria
archaea_contaminants <- subset_taxa(data, Kingdom == "Archaea") ## 5 ASVs of Archaea
#chloroplast_contaminants <- subset_taxa(data, Class == "Chloroplast")
chloroplast_contaminants <- subset_taxa(data, Order == "Chloroplast") ## 104 chloroplasts
eukaryota_contaminants <- subset_taxa(data, Kingdom == "Eukaryota")  ## 42 eukaryotic ASVs
sequences_not_assigned_to_kingdom <- subset_taxa(data, is.na(Kingdom)) ##drop 37 ASVs not assigned at Kingdom level
# ntaxa(chloroplast_contaminants)
```

Keep only bacterial taxa
```{r}
data.bac <- subset_taxa(data, Kingdom == "Bacteria")
```

Transform and rarefy
```{r}
#rarefy
data_rarefied <- rarefy_even_depth(data.bac, sample.size= 77213, rngseed=(12), replace=F)
#5 Samples removed
#transform
data_transformed <- transform_sample_counts(data.bac, function(x) x / sum(x) )
data.bac
data_rarefied
data_transformed
```
##Alpha Diversity 
```{r}
#Prep data
mic.assmblg <- data_rarefied
results <- estimate_richness(mic.assmblg, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(mic.assmblg)
```

```{r}
display.brewer.pal(n = 8, name = 'Dark2')
brewer.pal(n = 8, name = "Dark2")
#by time point
timept <- plot_richness(mic.assmblg, x = "Sampling_time", measures=c("Shannon","Simpson", "Observed"), color='Sampling_time') + guides(color=guide_legend(title="Sampling Time"))#, shape="Sampling_time")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
timept <- timept + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=10, angle=0),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Sampling Time") + theme(axis.text=element_text(size=12)) 
timept<-timept + scale_colour_manual(values = c( "#1B9E77", "#D95F02", "#7570B3", "#E7298A"))
timept


shapiro.test(aov(results$Shannon~d$Sampling_time)$residuals)
tp_shannon<-kruskal.test(results$Shannon~ factor(d$Sampling_time))
dunnTest(results$Shannon~ factor(d$Sampling_time), method = "bon")

shapiro.test(aov(results$Simpson~d$Sampling_time)$residuals)
tp_simpson<-kruskal.test(results$Simpson~ factor(d$Sampling_time))
dunnTest(results$Simpson~ factor(d$Sampling_time), method = "bon")

shapiro.test(aov(results$Observed~d$Sampling_time)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
tp_observed<-kruskal.test(results$Observed~ factor(d$Sampling_time))
dunnTest(results$Observed~ factor(d$Sampling_time), method = "bon")
```
By phenotype aka flowering time
```{r}
#by flowering time
ft <- plot_richness(mic.assmblg, x = "phenotype", measures=c("Shannon","Simpson", "Observed"), color='phenotype')  #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
ft <- ft + geom_boxplot() + theme_bw()
ft


#shapiro.test(aov(results$Shannon~d$phenotype)$residuals)
tp_shannon<-kruskal.test(results$Shannon~ factor(d$phenotype))
dunnTest(results$Shannon~ factor(d$phenotype), method = "bon")
#
#shapiro.test(aov(results$Simpson~d$phenotype)$residuals)
tp_simpson<-kruskal.test(results$Simpson~ factor(d$phenotype))
dunnTest(results$Simpson~ factor(d$phenotype), method = "bon")

#shapiro.test(aov(results$Observed~d$phenotype)$residuals)
tp_observed<-kruskal.test(results$Observed~ factor(d$phenotype))
dunnTest(results$Observed~ factor(d$phenotype), method = "bon")
```
By genotype
```{r}
#by genotype
sample_data(mic.assmblg)$genotype_base <-  factor(sample_data(mic.assmblg)$genotype_base, levels = c( "CS3797", "SALK_072930C", "CS6673", "CS6230", "CS9869"), ordered = T)
sample_data(mic.assmblg)$Genotype <-  factor(sample_data(mic.assmblg)$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

#if we want to look at differences among samples at time 1 (all in veg stage) we can subset to only time 1 and replot same stuff.
mic.assmblg_T1<-subset_samples(mic.assmblg, Sampling_time == "T1")

geno <- plot_richness(mic.assmblg_T1, x = "genotype_base", measures=c("Shannon","Simpson", "Observed"), color='Genotype') + guides(color=guide_legend(title="Genotype"))#, shape="Sampling_time")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
geno <- geno + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=8, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Genotype") + theme(axis.text=element_text(size=12)) 
#geno + scale_colour_manual(values = c("#CD6821","#158172","#214788","#F0E442", "#009E73", "#CC79A7")) 
geno <- geno + scale_colour_manual(values = c( "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2"))
geno



#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
##timept <- timept + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=10, angle=0),
#          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Sampling Time") + theme(axis.text=element_text(size=12)) 
#timept

#rotate axis
results_t1 <- estimate_richness(mic.assmblg_T1, measures = c('Shannon', 'Simpson', 'Observed'))
d_t1 <- sample_data(mic.assmblg_T1)

#shapiro.test(aov(results$Shannon~d$genotype)$residuals)
tp_shannon<-kruskal.test(results_t1$Shannon~ factor(d_t1$genotype))
dunnTest(results_t1$Shannon~ factor(d_t1$genotype), method = "bon")

#shapiro.test(aov(results$Simpson~d$genotype)$residuals)
tp_simpson<-kruskal.test(results_t1$Simpson~ factor(d_t1$genotype))
dunnTest(results_t1$Simpson~ factor(d_t1$genotype), method = "bon")

#shapiro.test(aov(results$Observed~d$genotype)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
tp_observed<-kruskal.test(results_t1$Observed~ factor(d_t1$genotype))
dunnTest(results_t1$Observed~ factor(d_t1$genotype), method = "bon")
```
flowering status
```{r}
display.brewer.all(colorblindFriendly = F)
display.brewer.pal(n = 8, name = 'Accent')
brewer.pal(n = 8, name = "Accent")

sample_data(mic.assmblg)$Developmental_stage <-  factor(sample_data(mic.assmblg)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting", "senesce"), ordered = T)
#by genotype
status <- plot_richness(mic.assmblg, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') + guides(color=guide_legend(title="Developmental Stage"))#, shape="Sampling_time")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
status <- status + geom_boxplot() + theme_bw() +theme(strip.text.x = element_text(size = 12, colour = "black", angle = 0)) +  theme(axis.text.x = element_text(color="black", size=8, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Developmental Stage") + theme(axis.text=element_text(size=12)) 
status <- status +scale_colour_manual(values = c("#7FC97F", "#BEAED4", "#FDC086", "#386CB0"))
status
#rotate axis

shapiro.test(aov(results$Shannon~d$status)$residuals)
tp_shannon<-kruskal.test(results$Shannon~ factor(d$status))
dunnTest(results$Shannon~ factor(d$status), method = "bon")

shapiro.test(aov(results$Simpson~d$status)$residuals)
tp_simpson<-kruskal.test(results$Simpson~ factor(d$status))
dunnTest(results$Simpson~ factor(d$status), method = "bon")

shapiro.test(aov(results$Observed~d$status)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
tp_observed<-kruskal.test(results$Observed~ factor(d$status))
dunnTest(results$Observed~ factor(d$status), method = "bon")
```

#Split by time point and look at flowering status within a given time point
```{r}

```


##Multivariate
Prep
```{r}
taxa_table<-data.frame(otu_table(data_transformed))
samp_data <- data.frame(sample_data(data_transformed))
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)

adonis(psdist ~ Genotype, data = data.frame((samp_data)), strata = "Genotype")
```

Time point and graph
```{r}
adonis(psdist ~ Sampling_time, data.frame((samp_data)), permutations = 1000)

pairwise<-pairwise.adonis2(taxa_table ~ Sampling_time, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
summary(pairwise)
pairwise

samp_data$Genotype <-  factor(samp_data$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

ord<-ord
#make the plot with everything 
d <- gg_ordiplot(ord, samp_data$Sampling_time, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipseT1 <- subset(df_ellipse, Group == "T1", droplevels= TRUE)
ellipseT2 <- subset(df_ellipse, Group == "T2", droplevels= TRUE)
ellipseT3 <- subset(df_ellipse, Group == "T3", droplevels= TRUE)
ellipseT4 <- subset(df_ellipse, Group == "T4", droplevels= TRUE)

#make the dataframe and subset out samples you dont want to plot
test<-d$df_ord
test$Sample_ID<-rownames(test)
Herbicides<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(Herbicides)<-c("Group", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, Herbicides)
#test$Group=NULL
names(test)<-c("x", "y","Time","SampleID", "Phenotype", "Genotype")

#+ scale_colour_manual(values = c( "#1B9E77", "#D95F02", "#7570B3", "#E7298A"))

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Time)  + geom_point(aes(color= Time, shape=Genotype)) + scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipseT1, aes(x=x, y=y), color="#1B9E77", linetype="solid", size=1.0) +
    geom_path(data= ellipseT2, aes(x=x, y=y), color="#D95F02", linetype="solid", size=1.0) +
  geom_path(data= ellipseT3, aes(x=x, y=y), color="#7570B3", linetype="solid", size=1.0) +
    geom_path(data= ellipseT4, aes(x=x, y=y), color="#E7298A", linetype="solid", size=1.0) 

#theme it on up
plot_test<- plot_test + theme_classic()
m<-plot_test 
#m <-m + annotate("text", x = -0.05, y = -0.012, label = "Time 2")
#m <-m + annotate("text", x = 0.01, y = -0.01, label = "Time 3")
#m <-m + annotate("text", x = 0.045, y = -0.023, label = "Time 1")
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Time: p < 0.001")
#m <- m + #ggtitle("NMDS of Infestation Stage and Soil Origin", ) +
#  theme(plot.title = element_text(hjust = 0.5, size = 22)) + labs(shape="Soil Origin", colour="Infestation Stage")
m <- m + labs(x= "NMDS2", y="NMDS1")
#m + guides(colour=guide_legend(override.aes=list(linetype=c(2,rep(1,times=2)))))
#t <- m + ggtitle("Ordination by Time") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
t <- m 
t
```
Genotype
```{r}
#run this if we want to subset to time 1:
data_transformed_t1<-subset_samples(data_transformed, Sampling_time =="T1")
taxa_table<-data.frame(otu_table(data_transformed_t1))
samp_data <- data.frame(sample_data(data_transformed_t1))
psdist_t1<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)



adonis(psdist_t1 ~ Genotype, data = data.frame((samp_data)), permutations = 100)
#not significant so no need to do pairwise comparisons. 
#pairwise<-pairwise.adonis2(taxa_table ~ time_point, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise
samp_data$Genotype <-  factor(samp_data$Genotype, levels = c( "CS3797 (TFL2-2, early)", "SALK_072930C (SVP-32, early)", "CS6673 (WT, WT)", "CS6230 (AP1-10, late)", "CS9869 (FT-10, late)"), ordered = T)

ord<-ord
#make the plot with everything 
d <- gg_ordiplot(ord, samp_data$Genotype, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipseG1 <- subset(df_ellipse, Group == "CS3797 (TFL2-2, early)", droplevels= TRUE)
ellipseG2 <- subset(df_ellipse, Group == "CS6230 (AP1-10, late)", droplevels= TRUE)
ellipseG3 <- subset(df_ellipse, Group == "CS6673 (WT, WT)", droplevels= TRUE)
ellipseG4 <- subset(df_ellipse, Group == "CS9869 (FT-10, late)", droplevels= TRUE)
ellipseG5 <- subset(df_ellipse, Group == "SALK_072930C (SVP-32, early)", droplevels= TRUE)


#make the dataframe and subset out samples you dont want to plot
test<-d$df_ord
test$Sample_ID<-rownames(test)
Herbicides<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(Herbicides)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, Herbicides)
#test$Group=NULL
names(test)<-c("x", "y","Genotype","SampleID", "Time", "Phenotype", "Genotype2")

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Genotype)  + scale_color_manual(values=c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2")) + geom_point(aes(color= Genotype))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
    geom_path(data= ellipseG1, aes(x=x, y=y), color="#E69F00", linetype="solid", size=1.0) +
    geom_path(data= ellipseG2, aes(x=x, y=y), color="#56B4E9", linetype="solid", size=1.0) +
    geom_path(data= ellipseG3, aes(x=x, y=y), color="#009E73", linetype="solid", size=1.0) +
    geom_path(data= ellipseG4, aes(x=x, y=y), color="#F0E442", linetype="solid", size=1.0) +
    geom_path(data= ellipseG5, aes(x=x, y=y), color="#0072B2", linetype="solid", size=1.0) 
#theme it on up
plot_test<- plot_test + theme_classic()
m<-plot_test 
#m <-m + annotate("text", x = -0.05, y = -0.012, label = "Time 2")
#m <-m + annotate("text", x = 0.01, y = -0.01, label = "Time 3")
#m <-m + annotate("text", x = 0.045, y = -0.023, label = "Time 1")
m <-m + annotate("text", x = 0.225, y = -0.34, label = "Genoptype: p  > 0.7")
m<- m + labs(x= "NMDS2", y="NMDS1")
#g <- m + ggtitle("Ordination by Genotype") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
g <- m 
g
```
Phenotype
```{r}
adonis(psdist ~  phenotype, data = data.frame((samp_data)), permutations = 100)
#not significant so no need to do pairwise comparisons. 
#pairwise<-pairwise.adonis2(taxa_table ~ time_point, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise

ord<-ord
#make the plot with everything 
d <- gg_ordiplot(ord, samp_data$phenotype, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipsep1 <- subset(df_ellipse, Group == "early", droplevels= TRUE)
ellipsep2 <- subset(df_ellipse, Group == "late", droplevels= TRUE)
ellipsep3 <- subset(df_ellipse, Group == "WT", droplevels= TRUE)



#make the dataframe and subset out samples you dont want to plot
test<-d$df_ord
test$Sample_ID<-rownames(test)
Herbicides<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(Herbicides)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, Herbicides)
#test$Group=NULL
names(test)<-c("x", "y","phenotype2","SampleID", "Time", "Phenotype", "Genotype")

#make the ggplot scatter plot
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Phenotype) + scale_color_manual(values=c("#F564E3", "#619CFF", "#F8766D", "#009E73", "#000000")) + geom_point(aes(color=Phenotype, shape = Genotype))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipsep1, aes(x=x, y=y), color="#F564E3", linetype="solid", size=1.0) +
    geom_path(data= ellipsep2, aes(x=x, y=y), color="#619CFF", linetype="solid", size=1.0) +
    geom_path(data= ellipsep3, aes(x=x, y=y), color="#F8766D", linetype="solid", size=1.0) 
   
#theme it on up
plot_test<- plot_test + theme_classic()
m<-plot_test 
#m <-m + annotate("text", x = -0.05, y = -0.012, label = "Time 2")
#m <-m + annotate("text", x = 0.01, y = -0.01, label = "Time 3")
#m <-m + annotate("text", x = 0.045, y = -0.023, label = "Time 1")
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Time: P  = 0.27")
m<- m + labs(x= "NMDS2", y="NMDS1")
p <- m + ggtitle("Ordination by Phenotype") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
p
```

testing with nesting by developmental stage or by sampling time
```{r}
adonis(psdist ~ Sampling_time, data= data.frame((samp_data)), strata = samp_data$Developmental_stage, permutations = 1000)
adonis(psdist ~ Sampling_time, data= data.frame((samp_data)), permutations = 1000)

adonis(psdist ~ Developmental_stage, data= data.frame((samp_data)), strata = samp_data$Sampling_time, permutations = 1000)
adonis(psdist ~ Developmental_stage, data= data.frame((samp_data)), permutations = 1000)
```


Flowering Status
```{r}
adonis(psdist ~ Sampling_time, data= data.frame((samp_data)), strata = samp_data$Developmental_stage, permutations = 1000)
adonis(psdist ~  Sampling_time, data= data.frame((samp_data)), permutations = 1000)

#if not significant so no need to do pairwise comparisons. 
pairwise<-pairwise.adonis2(taxa_table ~ Developmental_stage, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
summary(pairwise)
pairwise

ord<-ord
#make the plot with everything 
d <- gg_ordiplot(ord, samp_data$Developmental_stage, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
#pull out the ellipses
df_ellipse <- d$df_ellipse
ellipses1 <- subset(df_ellipse, Group == "senesce", droplevels= TRUE)
ellipses2 <- subset(df_ellipse, Group == "flowering", droplevels= TRUE)
ellipses3 <- subset(df_ellipse, Group == "fruiting", droplevels= TRUE)
#ellipses4 <- subset(df_ellipse, Group == "preflwr", droplevels= TRUE)
ellipses5 <- subset(df_ellipse, Group == "vegetative", droplevels= TRUE)

#+scale_colour_manual(values = c("#7FC97F", "#BEAED4", "#FDC086", "#386CB0"))

#make the dataframe and subset out samples you dont want to plot
test<-d$df_ord
test$Sample_ID<-rownames(test)
Herbicides<-data.frame(samp_data$Sampling_time, samp_data$phenotype, samp_data$Genotype, rownames(samp_data))
names(Herbicides)<-c("Time", "Phenotype", "Genotype", "Sample_ID")
test<-full_join(test, Herbicides)
#test$Group=NULL
names(test)<-c("x", "y","Developmental Stage","SampleID", "Time", "Phenotype", "Genotype")
test$`Developmental Stage` <- factor(test$`Developmental Stage`, levels = c("vegetative",  "flowering", "fruiting","senesce"))
#make the ggplot scatter plot
#plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=Developmental_stage) + scale_color_manual(values=c("#F564E3", "#619CFF", "#FDC086", "#386CB0")) + geom_point(aes(color= Developmental_stage, shape=Time))
plot_test<-ggplot(test, aes(x=test$x, y=test$y), color=`Developmental Stage`) + scale_color_manual(values=c("#7FC97F", "#BEAED4", "#F8766D","#386CB0" )) + geom_point(aes(color= `Developmental Stage`, shape=Time))
#add paths, color, and size, of the hulls
plot_test <- plot_test +
  geom_path(data= ellipses1, aes(x=x, y=y), color="#7FC97F", linetype="solid", size=1.0) +
    geom_path(data= ellipses2, aes(x=x, y=y), color="#BEAED4", linetype="solid", size=1.0) +
    geom_path(data= ellipses3, aes(x=x, y=y), color="#FDC086", linetype="solid", size=1.0) +
     #geom_path(data= ellipses4, aes(x=x, y=y), color="#009E73", linetype="solid", size=1.0) +
    geom_path(data= ellipses5, aes(x=x, y=y), color="#386CB0", linetype="solid", size=1.0) 
   
#theme it on up
plot_test<- plot_test + theme_classic()
m<-plot_test 
#m <-m + annotate("text", x = -0.05, y = -0.012, label = "Time 2")
#m <-m + annotate("text", x = 0.01, y = -0.01, label = "Time 3")
#m <-m + annotate("text", x = 0.045, y = -0.023, label = "Time 1")
m <-m + annotate("text", x = 0.4, y = -0.5, label = "Developmental Stage: p < 0.01")
m<- m + labs(x= "NMDS2", y="NMDS1")
s <- m #+ scale_fill_discrete(name = "New Legend Title")#+ ggtitle("Ordination by Developmental Stage") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
s
```

```{r}
grid.arrange(t, s, p, g)
```
#Split by time point and examine flowering status at each time point. 
```{r}
time1<- subset_samples(data_rarefied, Sampling_time == "T1")
time2<- subset_samples(data_rarefied, Sampling_time == "T2")
time3<- subset_samples(data_rarefied, Sampling_time == "T3")
time4<- subset_samples(data_rarefied, Sampling_time == "T4")

time1_t<- subset_samples(data_transformed, Sampling_time == "T1")
time2_t<- subset_samples(data_transformed, Sampling_time == "T2")
time3_t<- subset_samples(data_transformed, Sampling_time == "T3")
time4_t<- subset_samples(data_transformed, Sampling_time == "T4")
```

Diversity (alpha and beta) split by time point and examining impact of flowering status 
Time 1
```{r}
mic.assmblg <- time1
results <- estimate_richness(time1, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time1)

#sample_data(time1)$status <-  factor(sample_data(time1)$status, levels = c("veg", "preflwr"), ordered = T)

#by time point
time1_status_alpha <- plot_richness(time1, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time1_status_alpha <- time1_status_alpha + geom_boxplot() + theme_bw()
time1_status_alpha

#shapiro.test(aov(results$Shannon~d$time_point)$residuals)
t1_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

#shapiro.test(aov(results$Simpson~d$time_point)$residuals)
t1_simpson<-kruskal.test(results$Simpson~ factor(d$status))
dunnTest(results$Simpson~ factor(d$status), method = "bon")

#shapiro.test(aov(results$Observed~d$time_point)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
t1_observed<-kruskal.test(results$Observed~ factor(d$status))
dunnTest(results$Observed~ factor(d$status), method = "bon")



taxa_table<-otu_table(time1_t)
samp_data <- sample_data(time1_t)
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)

adonis(psdist ~  status , data = data.frame((samp_data)))
#if not significant so no need to do pairwise comparisons. 
#pairwise<-pairwise.adonis2(taxa_table ~ status, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise
```
Time 2
```{r}
mic.assmblg <- time2
results <- estimate_richness(time2, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time2)

sample_data(time2)$Developmental_stage <-  factor(sample_data(time2)$Developmental_stage, levels = c("vegetative", "flowering"), ordered = T)


#by time point 2 
time2_status_alpha <- plot_richness(time2, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='status') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time2_status_alpha <- time2_status_alpha + geom_boxplot() + theme_bw()
time2_status_alpha

#shapiro.test(aov(results$Shannon~d$time_point)$residuals)
t2_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$status), method = "bon")

#shapiro.test(aov(results$Simpson~d$time_point)$residuals)
t2_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$status), method = "bon")

#shapiro.test(aov(results$Observed~d$time_point)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
t2_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$status), method = "bon")



#taxa_table<-otu_table(time2_t)
#samp_data <- sample_data(time2_t)
#psdist<-parDist(as.matrix(taxa_table), method = "bray")
#ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
#stressplot(ord)

#adonis(psdist ~  status , data = data.frame((samp_data)))
#if not significant so no need to do pairwise comparisons. 
#pairwise<-pairwise.adonis2(taxa_table ~ status, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise
```

Time 3
```{r}
mic.assmblg <- time3
results <- estimate_richness(time3, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time3)

sample_data(time3)$Developmental_stage <-  factor(sample_data(time3)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting"), ordered = T)

#by time point
time3_status_alpha <- plot_richness(time3, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time3_status_alpha <- time3_status_alpha + geom_boxplot() + theme_bw()
time3_status_alpha

#shapiro.test(aov(results$Shannon~d$time_point)$residuals)
t3_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

#shapiro.test(aov(results$Simpson~d$time_point)$residuals)
t3_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

#shapiro.test(aov(results$Observed~d$time_point)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
t3_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")



#taxa_table<-otu_table(time3_t)
#samp_data <- sample_data(time3_t)
#psdist<-parDist(as.matrix(taxa_table), method = "bray")
#ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
#stressplot(ord)

#adonis(psdist ~  status , data = data.frame((samp_data)))
#if not significant so no need to do pairwise comparisons. 
#pairwise<-pairwise.adonis2(taxa_table ~ status, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise
```

Time 4
```{r}
mic.assmblg <- time4
results <- estimate_richness(time4, measures = c('Shannon', 'Simpson', 'Observed'))
d <- sample_data(time4)

sample_data(time4)$Developmental_stage <-  factor(sample_data(time4)$Developmental_stage, levels = c("vegetative", "flowering", "fruiting", "senesce"), ordered = T)


#by time point
time4_status_alpha <- plot_richness(time4, x = "Developmental_stage", measures=c("Shannon","Simpson", "Observed"), color='Developmental_stage') #, shape="time_point")
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
time4_status_alpha <- time4_status_alpha + geom_boxplot() + theme_bw()
time4_status_alpha

#shapiro.test(aov(results$Shannon~d$time_point)$residuals)
t4_shannon<-kruskal.test(results$Shannon~ factor(d$Developmental_stage))
dunnTest(results$Shannon~ factor(d$Developmental_stage), method = "bon")

#shapiro.test(aov(results$Simpson~d$time_point)$residuals)
t4_simpson<-kruskal.test(results$Simpson~ factor(d$Developmental_stage))
dunnTest(results$Simpson~ factor(d$Developmental_stage), method = "bon")

#shapiro.test(aov(results$Observed~d$time_point)$residuals)
#Meets normality assumption but we will use kruskall wallis for congruency
t4_observed<-kruskal.test(results$Observed~ factor(d$Developmental_stage))
dunnTest(results$Observed~ factor(d$Developmental_stage), method = "bon")



taxa_table<-otu_table(time4_t)
samp_data <- sample_data(time4_t)
psdist<-parDist(as.matrix(taxa_table), method = "bray")
ord<-metaMDS(taxa_table, distance = "bray", k=3, trymax = 100, previous.best = T)
stressplot(ord)

adonis(psdist ~  Developmental_stage , data = data.frame((samp_data)), permutations = 1000)
#if not significant so no need to do pairwise comparisons. 
pairwise<-pairwise.adonis2(taxa_table ~ Developmental_stage, data = data.frame(samp_data), perm=1000, p.adjust.methods="bonferroni")
#summary(pairwise)
#pairwise
```

##Indicator species analysis
Generate human readable taxonomic labels.
```{r}
# generate a vector containing the full taxonomy path for all OTUs
wholetax <- do.call(paste, c(as.data.frame(tax_table(data_transformed))
                  [c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus")], 
                  sep = "__"))  # to distinguish from "_" within tax ranks

# turn the otu_table into a data.frame
otu_export <- as.data.frame(otu_table(data_transformed))
tmp <- names(otu_export)
tmp2<-seq(1:nrow(data.frame(tmp)))

# paste wholetax and OTU_ids together
for(i in 1:length(tmp)){
names(tmp)[i] = paste(wholetax[i], tmp2[i], sep = "__")
}

# overwrite old names
names(otu_export) <- names(tmp)
```

AT=1 means the taxa only occurs in that group and in no others. BT= 1 means all samples in that group have that taxa. 

Indicator species analysis for time point.
```{#r}
indval_t <- multipatt(otu_export, samp_data$time_point, control = how(nperm = 1000), func = "indval")
summary(indval_t, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_t, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

#max.order constrains the associations to a single group where as above it can be associated with multiple groups
indval_1_t <- multipatt(otu_export, samp_data$time_point, control = how(nperm = 1000), max.order = 1, func = "indval")
summary(indval_1_t, alpha = 0.01, At = 0.5, Bt = 0.8, indvalcomp = T)
summary(indval_1_t, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

indval_2_t <- multipatt(otu_export, samp_data$time_point, control = how(nperm = 1000), max.order = 2, func = "indval")
summary(indval_2_t, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_2_t, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)
```

Indicator species analysis for genotype. 
```{#r}
indval_g <- multipatt(otu_export, samp_data$genotype, control = how(nperm = 1000), func = "indval")
summary(indval_g, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_g, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

#max.order constrains the associations to a single group where as above it can be associated with multiple groups
indval_1_g <- multipatt(otu_export, samp_data$genotype, control = how(nperm = 1000), max.order = 1, func = "indval")
summary(indval_1_g, alpha = 0.01, At = 0.5, Bt = 0.8, indvalcomp = T)
summary(indval_1_g, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

indval_2_g <- multipatt(otu_export, samp_data$genotype, control = how(nperm = 1000), max.order = 2, func = "indval")
summary(indval_2_g, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_2_g, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)
```

Indicator analysis for flowering status
```{#r}
indval_s <- multipatt(otu_export, samp_data$status, control = how(nperm = 1000), func = "indval")
summary(indval_s, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_s, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

#max.order constrains the associations to a single group where as above it can be associated with multiple groups
indval_1_s <- multipatt(otu_export, samp_data$status, control = how(nperm = 1000), max.order = 1, func = "indval")
summary(indval_1_s, alpha = 0.01, At = 0.5, Bt = 0.8, indvalcomp = T)
summary(indval_1_s, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)

indval_2_s <- multipatt(otu_export, samp_data$status, control = how(nperm = 1000), max.order = 2, func = "indval")
summary(indval_2_s, alpha = 0.01, At = 0.5, Bt = 0.5, indvalcomp = T)
summary(indval_2_s, alpha = 0.01, At = 0.7, Bt = 0.8 , indvalcomp = T)
```

Time point indicator species analysis with Deseq2 at the ESV level. This is not going to be used but will be inlcuded here for now. 
```{#r}
diagdds <- phyloseq_to_deseq2(data_rarefied, ~ time_point)
diagdds <- DESeq(diagdds, test="Wald", fitType="parametric")

#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T1", "T2"))
#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T1", "T3"))
#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T1", "T4"))
#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T2", "T3"))
#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T2", "T4"))
#res <- DESeq2::results(diagdds,  contrast = c("time_point", "T3", "T4"))


  
alpha = 0.01
sigtab <- res[which(res$padj < alpha), ]
sigtab <- cbind(as(sigtab, "data.frame"), as(tax_table(data_rarefied)[rownames(sigtab), ], "matrix"))
head(sigtab)

#sigtabT12<-sigtab
#write.csv(sigtabT12, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab12.csv")
#sigtabT1T3<-sigtab
#write.csv(sigtabT1T3, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab13.csv")
#sigtabT14<-sigtab
#write.csv(sigtabT14, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab14.csv")

#sigtabT23<-sigtab
#write.csv(sigtabT23, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab23.csv")
#sigtabT24<-sigtab
#write.csv(sigtabT24, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab24.csv")

#sigtabT34<-sigtab
#write.csv(sigtabT34, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab34.csv")
```
Too many taxa to make a clear graph. Not using currenlty but may at a later date. 
```{#r}
sigtab<-sigtabT1T3
# Phylum order
x = tapply(sigtab$log2FoldChange, sigtab$Phylum, function(x) max(x))
x = sort(x, TRUE)
sigtab$Phylum = factor(as.character(sigtab$Phylum), levels=names(x))
# Genus order
x = tapply(sigtab$log2FoldChange, sigtab$Genus, function(x) max(x))
x = sort(x, TRUE)
sigtab$Genus = factor(as.character(sigtab$Genus), levels=names(x))
ggplot(sigtab, aes(x=Genus, y=log2FoldChange, color=Phylum)) + geom_point(size=6) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))
```

Indicator analysis at the genus level for time point. 
```{r}
data_rarefied_genus <- tax_glom(data_rarefied, "Genus")

diagdds <- phyloseq_to_deseq2(data_rarefied_genus, ~ Sampling_time)
diagdds <- DESeq(diagdds, test="Wald", fitType="parametric")

res1 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T1", "T2"))
res2 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T1", "T3"))
res3 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T1", "T4"))
res4 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T2", "T3"))
res5 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T2", "T4"))
res6 <- DESeq2::results(diagdds,  contrast = c("Sampling_time", "T3", "T4"))


res<-res6
alpha = 0.01
sigtab <- res[which(res$padj < alpha), ]
sigtab <- cbind(as(sigtab, "data.frame"), as(tax_table(data_rarefied)[rownames(sigtab), ], "matrix"))
head(sigtab)

#sigtabT12<-sigtab
#write.csv(sigtabT12, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab12_f.csv")
#sigtabT1T3<-sigtab
#write.csv(sigtabT1T3, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab13_f.csv")
#sigtabT14<-sigtab
#write.csv(sigtabT14, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab14_f.csv")

#sigtabT23<-sigtab
#write.csv(sigtabT23, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab23_f.csv")
#sigtabT24<-sigtab
#write.csv(sigtabT24, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab24_f.csv")

#sigtabT34<-sigtab
#write.csv(sigtabT34, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/sigtab34_f.csv")
```

We need a long vector of colors to plot genus and family level bar plots. 
```{r}
#create super long color vector
col_vector <- c("#000000", "#FFFF00", "#1CE6FF", "#FF34FF", "#FF4A46", "#008941", "#006FA6", "#A30059",
        "#FFDBE5", "#7A4900", "#0000A6", "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87",
        "#5A0007", "#809693", "#FEFFE6", "#1B4400", "#4FC601", "#3B5DFF", "#4A3B53", "#FF2F80",
        "#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92", "#FF90C9", "#B903AA", "#D16100",
        "#DDEFFF", "#000035", "#7B4F4B", "#A1C299", "#300018", "#0AA6D8", "#013349", "#00846F",
        "#372101", "#FFB500", "#C2FFED", "#A079BF", "#CC0744", "#C0B9B2", "#C2FF99", "#001E09",
        "#00489C", "#6F0062", "#0CBD66", "#EEC3FF", "#456D75", "#B77B68", "#7A87A1", "#788D66",
        "#885578", "#FAD09F", "#FF8A9A", "#D157A0", "#BEC459", "#456648", "#0086ED", "#886F4C",
        
        "#34362D", "#B4A8BD", "#00A6AA", "#452C2C", "#636375", "#A3C8C9", "#FF913F", "#938A81",
        "#575329", "#00FECF", "#B05B6F", "#8CD0FF", "#3B9700", "#04F757", "#C8A1A1", "#1E6E00",
        "#7900D7", "#A77500", "#6367A9", "#A05837", "#6B002C", "#772600", "#D790FF", "#9B9700",
        "#549E79", "#FFF69F", "#201625", "#72418F", "#BC23FF", "#99ADC0", "#3A2465", "#922329",
        "#5B4534", "#FDE8DC", "#404E55", "#0089A3", "#CB7E98", "#A4E804", "#324E72", "#6A3A4C",
        "#83AB58", "#001C1E", "#D1F7CE", "#004B28", "#C8D0F6", "#A3A489", "#806C66", "#222800",
        "#BF5650", "#E83000", "#66796D", "#DA007C", "#FF1A59", "#8ADBB4", "#1E0200", "#5B4E51",
        "#C895C5", "#320033", "#FF6832", "#66E1D3", "#CFCDAC", "#D0AC94", "#7ED379", "#012C58",
        
        "#7A7BFF", "#D68E01", "#353339", "#78AFA1", "#FEB2C6", "#75797C", "#837393", "#943A4D",
        "#B5F4FF", "#D2DCD5", "#9556BD", "#6A714A", "#001325", "#02525F", "#0AA3F7", "#E98176",
        "#DBD5DD", "#5EBCD1", "#3D4F44", "#7E6405", "#02684E", "#962B75", "#8D8546", "#9695C5",
        "#E773CE", "#D86A78", "#3E89BE", "#CA834E", "#518A87", "#5B113C", "#55813B", "#E704C4",
        "#00005F", "#A97399", "#4B8160", "#59738A", "#FF5DA7", "#F7C9BF", "#643127", "#513A01",
        "#6B94AA", "#51A058", "#A45B02", "#1D1702", "#E20027", "#E7AB63", "#4C6001", "#9C6966",
        "#64547B", "#97979E", "#006A66", "#391406", "#F4D749", "#0045D2", "#006C31", "#DDB6D0",
        "#7C6571", "#9FB2A4", "#00D891", "#15A08A", "#BC65E9", "#FFFFFE", "#C6DC99", "#203B3C",

        "#671190", "#6B3A64", "#F5E1FF", "#FFA0F2", "#CCAA35", "#374527", "#8BB400", "#797868",
        "#C6005A", "#3B000A", "#C86240", "#29607C", "#402334", "#7D5A44", "#CCB87C", "#B88183",
        "#AA5199", "#B5D6C3", "#A38469", "#9F94F0", "#A74571", "#B894A6", "#71BB8C", "#00B433",
        "#789EC9", "#6D80BA", "#953F00", "#5EFF03", "#E4FFFC", "#1BE177", "#BCB1E5", "#76912F",
        "#003109", "#0060CD", "#D20096", "#895563", "#29201D", "#5B3213", "#A76F42", "#89412E",
        "#1A3A2A", "#494B5A", "#A88C85", "#F4ABAA", "#A3F3AB", "#00C6C8", "#EA8B66", "#958A9F",
        "#BDC9D2", "#9FA064", "#BE4700", "#658188", "#83A485", "#453C23", "#47675D", "#3A3F00",
        "#061203", "#DFFB71", "#868E7E", "#98D058", "#6C8F7D", "#D7BFC2", "#3C3E6E", "#D83D66",

        "#2F5D9B", "#6C5E46", "#D25B88", "#5B656C", "#00B57F", "#545C46", "#866097", "#365D25",
        "#252F99", "#00CCFF", "#674E60", "#FC009C", "#92896B")
```

Abundance bar plots for time point only including indicator taxa. Taxa graphed here must be an indicator in atleast one comparison. 
```{r}
data_indic<-subset_taxa(physeq = data_rarefied_genus, colnames(data_rarefied_genus@otu_table) %in% c(rownames(sigtabT12), rownames(sigtabT1T3), rownames(sigtabT14), rownames(sigtabT23), rownames(sigtabT24), rownames(sigtabT34)))

data_indic_table<-data.frame(otu_table(data_indic))
data_indic_samp_data<-data.frame(sample_data(data_indic))

#check to make sure a postive number in logchange indicates the second category is higher.
#boxplot(data_indic_table$ACAGAGGGTGCAAGCGTTAATCGGATTTACTGGGCGTAAAGCGTGTGTAGGTGGTTGGGAAAGTCAATTGTGAAATCCCCGGGCTTAACTCGGGAACTGCTTTTGATACTGTCTGACTAGAATTCGGTAGAGGGAGGCGGAACTCCAGGTGTAGCGGTGAAATGCGTAGATATCTGGAAGAACACCAATGGCGAAGGCAACCTCCTGGGCCTGAATTGACACTGAGACACGAAAGCGTGGGGATCAAACAGGATTAGATACCCTGGTAGTCCACGCCGTAAACGATGACAACTTGACGTCGGTTTGCTCTGCGAATCGGTGTCGTAGCTAACGCGATAAGTTGTCCGCCTGGGGAGTACGGCCGCAAGGTTGAA ~ data_indic_samp_data$time_point )


ps <- tax_glom(data_indic, "Family")
#ps<-data_indic
ps0 <- transform_sample_counts(ps, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "Sampling_time")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
#col_vector<-c(col_vector , col_vector, col_vector, col_vector)
#all_indic_bar_plot<-plot_bar(ps2, fill="Genus") + scale_fill_manual(values = col_vector)
#all_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector)
all_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector)


ps <- tax_glom(data_indic, "Family")
ps0  <- transform_sample_counts(ps, function(x) x / sum(x) )
ps0_5 <- filter_taxa(ps0, function(x) sum(x) > 0.5, TRUE)
ps1 <- merge_samples(ps0_5, "Sampling_time")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
#col_vector<-c(col_vector , col_vector, col_vector, col_vector)
#common_indic_bar_plot<-plot_bar(ps2, fill="Genus") + scale_fill_manual(values = col_vector)
#common_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector) + ggtitle("Common Indicator at Family Level") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
common_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector) 
common_indic_bar_plot_family <- common_indic_bar_plot_family + theme_bw() +  theme(axis.text.x = element_text(color="black", size=10, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Sampling Time") + ylab("Relative Abundance") + theme(axis.text=element_text(size=12)) 

common_indic_bar_plot_family
```

Unique indicator taxa by time point. This also contains all indicators but i figure only those unique to a given time would be of interest. I widdle this list down to taxa that are only indicators of a single time point. 
```{r}
data_indic<-subset_taxa(physeq = data_rarefied_genus, colnames(data_rarefied_genus@otu_table) %in% c(rownames(sigtabT12), rownames(sigtabT1T3), rownames(sigtabT14), rownames(sigtabT23), rownames(sigtabT24), rownames(sigtabT34)))

data_indic_table<-data.frame(otu_table(data_indic))
data_indic_samp_data<-data.frame(sample_data(data_indic))

#check to make sure a postive number in logchange indicates the second category is higher.
boxplot(data_indic_table$ACGAACCGAGCGAACGTTGTTCGGAATCACTGGGCTTAAAGGGCGCGTAGGCGGGCGGCTAAGTCTGTGGTGAAATCCTCCAGCTCAACTGGAGAACTGCCATGGATACTGGTTGTCTCGAGGAAGGTAGGGGTATGCGGAACTATCGGTGGAGCGGTGAAATGCGTTGATATCGATAGGAACTCCGGTGGCGAAGGCGGCATACTGGACCTTTTCTGACGCTGAGGCGCGAAAGCCAGGGGAGCAAACGGGATTAGATACCCCGGTAGTCCTGGCCCTAAACGATGGGTACTAGCTAGTAGGGTTCACATGGCTTTACTGGCGAAGCAAAAGTGCTAAGTACCCCGCCTGGGGAGTATGGTCGCAAGGCTGAA ~ data_indic_samp_data$time_point)


#tableing the indicator taxa time
#time 1 indicators 
t1_2_sig<-sigtabT12[sigtabT12$log2FoldChange >= 0,]
a<-rownames(t1_2_sig)

t1_3_sig<-sigtabT1T3[sigtabT1T3$log2FoldChange >= 0,]
b<-rownames(t1_3_sig)

t1_4_sig<-sigtabT14[sigtabT14$log2FoldChange >= 0,]
c<-rownames(t1_4_sig)
d<-c(a,b,c)
e<-unique(d)

Time1_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% e)
#ps1 <- merge_samples(Time1_indicators, "time_point")
#ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
#plot_bar(ps2, fill = "Family") + scale_fill_manual(values = col_vector)

library(metagMisc)
Time1_test<-phyloseq_to_df(Time1_indicators, addtax = T)
sort(table(Time1_test$Phylum))

#time 2 indicators 
t2_1_sig<-sigtabT12[sigtabT12$log2FoldChange <= 0,]
a<-rownames(t2_1_sig)
t2_3_sig<-sigtabT23[sigtabT23$log2FoldChange >= 0,]
b<-rownames(t2_3_sig)
t2_4_sig<-sigtabT24[sigtabT24$log2FoldChange >= 0,]
c<-rownames(t2_4_sig)
d<-c(a,b,c)
e<-unique(d)
Time2_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% e)
Time2_test<-phyloseq_to_df(Time2_indicators, addtax = T)
sort(table(Time2_test$Phylum))

#time 3 indicators
t3_1_sig<-sigtabT1T3[sigtabT1T3$log2FoldChange <= 0,]
a<-rownames(t3_1_sig)
t3_2_sig<-sigtabT23[sigtabT23$log2FoldChange <= 0,]
b<-rownames(t3_2_sig)
t3_4_sig<- sigtabT34[sigtabT34$log2FoldChange >= 0,]
c<-rownames(t3_4_sig)
d<-c(a,b,c)
e<-unique(d)
Time3_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% e)
Time3_test<-phyloseq_to_df(Time3_indicators, addtax = T)
sort(table(Time3_test$Phylum))

#time 4 indicators
t4_1_sig<-sigtabT14[sigtabT14$log2FoldChange <= 0,]
a<-rownames(t4_1_sig)
t4_2_sig<-sigtabT24[sigtabT24$log2FoldChange <= 0,]
b<-rownames(t4_2_sig)
t4_3_sig<- sigtabT34[sigtabT34$log2FoldChange <= 0,]
c<-rownames(t4_3_sig)
d<-c(a,b,c)
e<-unique(d)
Time4_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% e)
Time4_test<-phyloseq_to_df(Time4_indicators, addtax = T)
sort(table(Time4_test$Phylum))
str(Time4_test)

#False is not found in any other indicator set
table(Time1_test$OTU %in% c(Time2_test$OTU,Time3_test$OTU, Time4_test$OTU))
which(!Time1_test$OTU %in% c(Time2_test$OTU,Time3_test$OTU, Time4_test$OTU))
unique_to_T1<-Time1_test[which(!Time1_test$OTU %in% c(Time2_test$OTU,Time3_test$OTU, Time4_test$OTU)),]
table(unique_to_T1$Phylum)
table(unique_to_T1$Class)
table(unique_to_T1$Order)
table(unique_to_T1$Family)

table(Time2_test$OTU %in% c(Time1_test$OTU,Time3_test$OTU, Time4_test$OTU))
which(!Time2_test$OTU %in% c(Time1_test$OTU,Time3_test$OTU, Time4_test$OTU))
unique_to_T2<-Time2_test[which(!Time2_test$OTU %in% c(Time1_test$OTU,Time3_test$OTU, Time4_test$OTU)),]
table(unique_to_T2$Phylum)
table(unique_to_T2$Class)
table(unique_to_T2$Order)
table(unique_to_T2$Family)

table(Time3_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time4_test$OTU))
which(!Time3_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time4_test$OTU))
unique_to_T3 <- Time3_test[which(!Time3_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time4_test$OTU)),]
table(unique_to_T3$Phylum)
table(unique_to_T3$Class)
table(unique_to_T3$Order)
table(unique_to_T3$Family)

table(Time4_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time3_test$OTU))
which(!Time4_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time3_test$OTU))
unique_to_T4 <- Time4_test[which(!Time4_test$OTU %in% c(Time1_test$OTU,Time2_test$OTU, Time3_test$OTU)),]
table(unique_to_T4$Phylum)
table(unique_to_T4$Class)
table(unique_to_T4$Order)
table(unique_to_T4$Family)


unique_to_single_time<-rbind(unique_to_T1, unique_to_T2, unique_to_T3, unique_to_T4)#
#write.csv(unique_to_single_time, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/unique_to_single_time.csv")

```

Not using currently but will keep for later date if needed 
```{#r}
#make box n whisker plot of phylum for summarized time point data
silk_workingr <- transform_sample_counts(time_merged, function(x) x/sum(x))
# agglomerate taxa
glom <- tax_glom(silk_workingr, taxrank = 'Phylum')
#create dataframe
dat <- psmelt(glom)
#make phylum a character
dat$Phylum <- as.character(dat$Phylum)
library(plyr)
medians <- ddply(dat, ~Phylum, function(x) c(median=median(x$Abundance)))
remainder <- medians[medians$median <= 0.0001,]$Phylum
dat[dat$Phylum %in% remainder,]$Phylum <- 'Remainder'
ggplot(dat,
       aes(x=Phylum,
           y=Abundance)) + geom_boxplot() + coord_flip()
```

Abundance bar plots by time -- includes all taxa
```{r}

#all taxa reduced to phylum
ps <- tax_glom(data.bac, "Family")
ps0 <- transform_sample_counts(ps, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "Sampling_time")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
time_Class<-plot_bar(ps2, fill="Class") + scale_fill_manual(values = col_vector)
time_Order<-plot_bar(ps2, fill="Order") + scale_fill_manual(values = col_vector)
time_Phylum<-plot_bar(ps2, fill="Phylum") + scale_fill_manual(values = col_vector)
time_Family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector)
```

Indicator analysis for genotype 
```{r}
data_rarefied_genus <- tax_glom(data_rarefied, "Genus")

diagdds <- phyloseq_to_deseq2(data_rarefied_genus, ~ genotype)
diagdds <- DESeq(diagdds, test="Wald", fitType="parametric")

#no indicator taxa at the family level.

res1 <- DESeq2::results(diagdds,  contrast = c("genotype", "SALK_072930C", "CS3797")) # none
res2 <- DESeq2::results(diagdds,  contrast = c("genotype", "SALK_072930C", "CS6230")) # 1
res3 <- DESeq2::results(diagdds,  contrast = c("genotype", "SALK_072930C", "CS9869")) # 2
res4 <- DESeq2::results(diagdds,  contrast = c("genotype", "SALK_072930C", "CS6673")) # none

res5 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS3797", "CS6230")) # 1
res6 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS3797", "CS9869")) #2
res7 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS3797", "CS6673")) # none

res8 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS6230", "CS9869")) # none
res9 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS6230", "CS6673")) # none

res10 <- DESeq2::results(diagdds,  contrast = c("genotype", "CS9869", "CS6673")) # none
  
res<-res6
alpha = 0.01
sigtab <- res[which(res$padj < alpha), ]
sigtab <- cbind(as(sigtab, "data.frame"), as(tax_table(data_rarefied)[rownames(sigtab), ], "matrix"))
head(sigtab)

#hashed out so i cant over write accidentaly. Each output table gets its own sigtab for later. 
#sigtab1<- sigtab 
#write.csv(sigtab1, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/SALK072930C_CS6230.csv")
#sigtab2<- sigtab #
#write.csv(sigtab2, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/SALK072930C_CS9869.csv")
#sigtab3<- sigtab #
#write.csv(sigtab3, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/CS3797_CS6230.csv")
#sigtab4<- sigtab #
#write.csv(sigtab4, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/CS3797_CS9869.csv")
#sigtab5<- sigtab
#sigtab6<- sigtab
#sigtab7<- sigtab
#sigtab8<- sigtab
#sigtab9<- sigtab
#sigtab10<- sigtab

#will write out if something is interesting
#sigtab12<-sigtab
#write.csv(sigtabT12, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab")
#sigtabT1T3<-sigtab
#write.csv(sigtabT1T3, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab13_g.csv")
#sigtabT14<-sigtab
#write.csv(sigtabT14, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab14_g.csv")

#sigtabT23<-sigtab
#write.csv(sigtabT23, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab23_g.csv")
#sigtabT24<-sigtab
#write.csv(sigtabT24, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab24_g.csv")

#sigtabT34<-sigtab
#write.csv(sigtabT34, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/sigtab34_g.csv")
```

Abundance bar plots by genotype -- includes all taxa
```{r}
ps <- tax_glom(data.bac, "Family")
ps0 <- transform_sample_counts(ps, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "Genotype")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
geno_class <-plot_bar(ps2, fill="Class") + scale_fill_manual(values = col_vector)
geno_order <-plot_bar(ps2, fill="Order") + scale_fill_manual(values = col_vector)
geno_phylum <-plot_bar(ps2, fill="Phylum") + scale_fill_manual(values = col_vector)
geno_family <-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector)
```

With only a few indicator taxa for genotype i didnt bother making the bar plots for them. 

Indicator analysis for flowering status
```{r}
data_rarefied_genus <- tax_glom(data_rarefied, "Genus")

diagdds <- phyloseq_to_deseq2(data_rarefied_genus, ~ Developmental_stage)
diagdds <- DESeq(diagdds, test="Wald", fitType="parametric")

res1 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "senesce", "flowering")) # 1
res2 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "senesce", "fruiting")) # 2
res3 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "senesce", "vegetative")) # 3

res4 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "flowering", "fruiting")) # 4

res5 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "flowering", "vegetative")) # 5

res6 <- DESeq2::results(diagdds,  contrast = c("Developmental_stage", "fruiting", "vegetative")) # 6

res<-res4
  
alpha = 0.01
sigtab <- res[which(res$padj < alpha), ]
sigtab <- cbind(as(sigtab, "data.frame"), as(tax_table(data_rarefied)[rownames(sigtab), ], "matrix"))
View(sigtab)

#hashed out so i cant over write accidentaly. Each output table gets its own sigtab for later. 
#sigtab1<- sigtab #
#write.csv(sigtab1, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/done_flower.csv")
#sigtab2<- sigtab #
#write.csv(sigtab2, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/done_fruit.csv")
#sigtab3<- sigtab #
#write.csv(sigtab3, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/done_veg.csv")


#sigtab4<- sigtab
#write.csv(sigtab4, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis//flwr_fruit.csv")

#sigtab5<- sigtab
#write.csv(sigtab5, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/flwr_veg.csv")

#sigtab6<- sigtab
#write.csv(sigtab6, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/fruit_veg.csv")

```

Abundance bar plots for flowering status only including indicator taxa
```{r}
data_indic<-subset_taxa(physeq = data_rarefied_genus, colnames(data_rarefied_genus@otu_table) %in% c(rownames(sigtab1), rownames(sigtab2), rownames(sigtab3), rownames(sigtab4), rownames(sigtab5), rownames(sigtab6)))

sample_data(data_indic)$Developmental_stage <-  factor(sample_data(data_indic)$Developmental_stage, levels = c("vegetative" , "flowering", "fruiting", "senesce"), ordered = T)

ps <- tax_glom(data_indic, "Genus")
#ps<-data_indic
ps0 <- transform_sample_counts(ps, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "Developmental_stage")
ps1@sam_data$status<-factor(rownames(sample_data(ps1)), levels = c("vegetative" , "flowering", "fruiting", "senesce"), ordered = T)

ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
#col_vector<-c(col_vector , col_vector, col_vector, col_vector)
#all_indic_bar_plot<-plot_bar(ps2, fill="Genus") + scale_fill_manual(values = col_vector)
sample_data(ps2)$status <-  factor(sample_data(ps2)$status, levels = c("vegetative" , "flowering", "fruiting", "senesce"), ordered = T)

all_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector)
all_indic_bar_plot_family$data$Sample <- factor(all_indic_bar_plot_family$data$Sample, levels = c("vegetative" , "flowering", "fruiting", "senesce"), ordered = T)
print(all_indic_bar_plot_family)
all_indic_bar_plot_phylum<-plot_bar(ps2, fill="Phylum") + scale_fill_manual(values = col_vector)
all_indic_bar_plot_phylum$data$Sample <- factor(all_indic_bar_plot_family$data$Sample, levels = c("vegetative" , "flowering", "fruiting", "senesce"), ordered = T)
print(all_indic_bar_plot_phylum)

ps <- tax_glom(data_indic, "Family")
ps0  <- transform_sample_counts(ps, function(x) x / sum(x) )
ps0_5 <- filter_taxa(ps0, function(x) sum(x) > 0.5, TRUE)
ps1 <- merge_samples(ps0_5, "Developmental_stage")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
#col_vector<-c(col_vector , col_vector, col_vector, col_vector)
#common_indic_bar_plot<-plot_bar(ps2, fill="Genus") + scale_fill_manual(values = col_vector)
common_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector) #+ ggtitle("Common Indicator at Family Level") + theme(plot.title = element_text(hjust = 0.5, size = 22))  
common_indic_bar_plot_family$data$Sample <- factor(common_indic_bar_plot_family$data$Sample, levels = c("vegetative" , "flowering", "fruiting", "senesce"))
#print(common_indic_bar_plot_family)
#common_indic_bar_plot_family<-plot_bar(ps2, fill="Family") + scale_fill_manual(values = col_vector) 
#Pheno <- Pheno + scale_colour_manual(values = c("#CD6821","#CD6821","#CD6821","#CD6821","#158172","#158172","#158172","#158172","#214788","#214788","#214788","#214788")) 
common_indic_bar_plot_family <- common_indic_bar_plot_family + theme_bw() +  theme(axis.text.x = element_text(color="black", size=10, angle=45, hjust=1),
          axis.text.y = element_text(color="black", size=10, angle=45)) + scale_x_discrete(name ="Developmental Stage") + ylab("Relative Abundance") + theme(axis.text=element_text(size=12)) 
common_indic_bar_plot_family
```

Taxa unique to a single flowering stage.
```{r}
data_indic<-subset_taxa(physeq = data_rarefied_genus, colnames(data_rarefied_genus@otu_table) %in% c(rownames(sigtab1), rownames(sigtab2), rownames(sigtab3), rownames(sigtab4), rownames(sigtab5), rownames(sigtab6)))


data_indic_table<-data.frame(otu_table(data_indic))
data_indic_samp_data<-data.frame(sample_data(data_indic))

#check to make sure a postive number in logchange indicates the first()? category is higher.
boxplot(data_indic_table$ACGGAGGGTGCAAGCGTTATCCGGATTTATTGGGTTTAAAGGGTCCGTAGGCGGACCTGTAAGTCAGTGGTGAAATCTCATAGCTTAACTATGAAACTGCCATTGATACTGCAGGTCTTGAGTAAATTTGAAGTGGCTGGAATAAGTAGTGTAGCGGTGAAATGCATAGATATTACTTAGAACACCAATTGCGAAGGCAGGTCACTAAGATTTAACTGACGCTGAGGGACGAAAGCGTGGGGAGCGAACAGGATTAGATACCCTGGTAGTCCACGCCGTAAACGATGCTAACTCGTTTTTGGATTTTCGGATTCAGAGACCAAGCGAAAGTGATAAGTTAGCCACCTGGGGAGTACGTCCGCAAGGATGAA ~ data_indic_samp_data$status)

#Flower status indicators 

#tableing the indicator taxa time
#done status indicators 
done_flwr <- sigtab1[sigtab1$log2FoldChange >= 0,]
done_flwr$Indicator<-paste("done_flwr")
a<-rownames(done_flwr)

done_fruit<-sigtab2[sigtab2$log2FoldChange >= 0,]
b<-rownames(done_fruit)

done_veg<-sigtab3[sigtab3$log2FoldChange >= 0,]
c<-rownames(done_veg)

e<-c(a,b,c)
f<-unique(e)

done_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% f)
library(metagMisc)
done_test<-phyloseq_to_df(done_indicators, addtax = T)
sort(table(done_test$Phylum))

#Flower indicators:

flwr_done<-sigtab1[sigtab1$log2FoldChange <= 0,]
flwr_done$Indicator<-paste("flower_done")
a<-rownames(flwr_done)
flwr_fruit<-sigtab4[sigtab4$log2FoldChange >= 0,]
b<-rownames(flwr_fruit)
flwr_veg<-sigtab5[sigtab5$log2FoldChange >= 0,]
d<-rownames(flwr_veg)

e<-c(a,b,d)
f<-unique(e)

flwr_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% f)
flwr_test<-phyloseq_to_df(flwr_indicators, addtax = T)
sort(table(flwr_test$Phylum))

#Fruit indicators
fruit_done<-sigtab2[sigtab2$log2FoldChange <= 0,]
a<-rownames(fruit_done)
fruit_flwr<-sigtab4[sigtab4$log2FoldChange <= 0,]
b<-rownames(fruit_flwr)

fruit_veg<- sigtab6[sigtab6$log2FoldChange >= 0,]
d<-rownames(fruit_veg)

e<-c(a,b,d)
f<-unique(e)

fruit_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% f)
fruit_test<-phyloseq_to_df(fruit_indicators, addtax = T)
sort(table(fruit_test$Phylum))


#Veg indicators
veg_done<-sigtab3[sigtab3$log2FoldChange <= 0,]
a<-rownames(veg_done)
veg_flwr<-sigtab5[sigtab5$log2FoldChange <= 0,]
b<-rownames(veg_flwr)
veg_fruit<- sigtab6[sigtab6$log2FoldChange <= 0,]
c<-rownames(veg_fruit)


e<-c(a,b,c)
f<-unique(e)

veg_indicators<- subset_taxa(physeq = data_indic, colnames(data_indic@otu_table) %in% f)
veg_test<-phyloseq_to_df(veg_indicators, addtax = T)
sort(table(veg_test$Phylum))


#False is not found in any other indicator set
#done
table(done_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, veg_test$OTU))
which(!done_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, veg_test$OTU))
unique_to_done<-done_test[which(!done_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, veg_test$OTU)),]
table(unique_to_done$Phylum)
table(unique_to_done$Class)
table(unique_to_done$Order)
table(unique_to_done$Family)

#flwr
table(flwr_test$OTU %in% c(done_test$OTU,fruit_test$OTU, veg_test$OTU))
which(!flwr_test$OTU %in% c(done_test$OTU,fruit_test$OTU, veg_test$OTU))
unique_to_flwr<-flwr_test[which(!flwr_test$OTU %in% c(done_test$OTU,fruit_test$OTU, veg_test$OTU)),]
table(unique_to_flwr$Phylum)
table(unique_to_flwr$Class)
table(unique_to_flwr$Order)
table(unique_to_flwr$Family)

#veg
table(veg_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, done_test$OTU))
which(!veg_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, done_test$OTU))
unique_to_veg<-veg_test[which(!veg_test$OTU %in% c(flwr_test$OTU,fruit_test$OTU, done_test$OTU)),]
table(unique_to_veg$Phylum)
table(unique_to_veg$Class)
table(unique_to_veg$Order)
table(unique_to_veg$Family)


#fruit
table(fruit_test$OTU %in% c(flwr_test$OTU,done_test$OTU, veg_test$OTU))
which(!fruit_test$OTU %in% c(flwr_test$OTU,done_test$OTU, veg_test$OTU))
unique_to_fruit<-done_test[which(!fruit_test$OTU %in% c(flwr_test$OTU,done_test$OTU, veg_test$OTU)),]
table)$Phylum)
table(unique_to_fruit$Class)
table(unique_to_fruit$Order)
table(unique_to_fruit$Family)


all_status_indicator<-read.csv("/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/Status_indicators.csv")



unique_idics_status<- all_status_indicator[all_status_indicator$X %in% c(unique_to_done$OTU, unique_to_flwr$OTU, unique_to_fruit$OTU, unique_to_veg$OTU),] 

write.csv(unique_idics_status, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/Unique_indics_status.csv")

unique_to_done_indic_table<-all_status_indicator[all_status_indicator$X %in% unique_to_done$OTU,]

unique_to_flwr_indic_table<-all_status_indicator[all_status_indicator$X %in% unique_to_flwr$OTU,]

unique_to_fruit_indic_table<-all_status_indicator[all_status_indicator$X %in% unique_to_fruit$OTU,]

unique_to_veg_indic_table<-all_status_indicator[all_status_indicator$X %in% unique_to_veg$OTU,]

unique_to_single_veg_status<-rbind(unique_to_done, unique_to_flwr, unique_to_fruit, unique_to_veg)

write.csv(unique_to_single_veg_status, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/unique_to_single_status.csv")

```

Unique and shared taxa by time point. I'm not sure exactly how we should pursue this but it could be a good idea. Unique taxa to a stage suggest turnover and provide some sort of evidence for sucession.
```{r}
unique_to_t_point<-unique_taxa(data_transformed, treatment = "time_point")
str(unique_to_t_point)
9793-1348-441-1304-1094
#5606 taxa shared between atleast two time points
unique_to_g_type<-unique_taxa(data_transformed, treatment = "genotype")
str(unique_to_g_type)
9793-797-909-640-739-756
#there are 5952 taxa shared between atleast two genotypes
time_merged <-merge_samples(data.bac, "time_point")

```
Relative abundance bar plot of those taxa occuring in the unique to list.
```{r}
vec <- Reduce(c,unique_to_t_point)
vec
ps_unique<-subset_taxa(physeq = data.bac, colnames(data.bac@otu_table) %in% vec)

library(RColorBrewer)
n <- 74
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
pie(rep(1,n), col=sample(col_vector, n))

#only taxa unique to one time point. 
# We can revist this and decide what might be useful to visualize. 
ps <- tax_glom(ps_unique, "Class")
ps0 <- transform_sample_counts(ps, function(x) x / sum(x))
ps1 <- merge_samples(ps0, "time_point")
ps2 <- transform_sample_counts(ps1, function(x) x / sum(x))
plot_bar(ps2, fill="Class") + scale_fill_manual(values = col_vector)
```



> all_status_indicator<-read.csv("/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/Status_indicators.csv")
> View(all_status_indicator)
> unique_idics_status<- all_status_indicator[all_status_indicator$X %in% c(unique_to_done$OTU, unique_to_flwr$OTU, unique_to_fruit$OTU, unique_to_veg$OTU),] 
> unique_idics_status
> write.csv(unique_idics_status, "/Users/gordoncuster/Desktop/Manuscript Submissions/SuccessionFloweringTime/SuccessionFloweringTime/May_Updated_Meta_data/IndicatorAnalysis/Unique_indics_status.csv")